\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Technical Lead}
    {Zenparent}
    {Bangalore, India}
    {May. 2015 - Present}
    {
      \begin{cvitems}
        \item {Implemented Web Scrapers and ETL tools to aid faster content creation. Used Scrapy and Xpath for scraping purposes.}
        \item {Developed a cross-platform mobile application using Apache Cordova, React JS, Redux for state management and Onsen UI for providing the native mobile experience. The app is available on \href{https://play.google.com/store/apps/details?id=com.zenparent.mobileapp}{\textit{\textbf{Playstore}}} and \href{https://itunes.apple.com/us/app/zenparent/id1221296168}{\textit{\textbf{Appstore}}}.}
        \item {Implemented a real-time chat system using Pusher, a Websocket service over cloud.}
        \item {Developed an article recommendation system using NLP techniques like keyword extraction and Apache Solr MoreLikeThis search component for querying articles with best keywords match.}
        \item {Built and deployed service infrastructure comprising of Load Balanced Web Servers with a Shared NFS, Memcached for Page and Object caching, Apache Solr as an Indexing Server and CDN for serving static assets using AWS stack(EC2,Route 53, CloudFront, RDS, ElastiCache).}
        \item {Implemented the website UI and backend services for the web and mobile clients.}
    \end{cvitems}
    }
   \cventry
    {Freelance Consultant}
    {Athletto}
    {Bangalore, India}
    {Nov. 2016 - May. 2017}
    {
      \begin{cvitems}
        \item {Designed and implemented a REST service for the customer wallet module using Laravel.}
        \item{Implemented a generic Laravel SMS Driver to support a variety of SMS service providers.}
      \end{cvitems}
    }

\end{cventries}
